Study 1

### 2022-01-07 code/analysis.Rmd
study 1 2x2 data

---
title: "BoS pilot"
output:
  html_document: 
    toc: true
---

# TODO

@@

##Data import constants
data_location="data/pilot211209"

date_start=lubridate::ymd('2021-12-09')

@@

# d.players <- read_csv(here(data_location, 'players.csv')) %>%
#   rename(playerId=`_id`) %>%
#   select(data.bonus, playerId,id) %>%
#   mutate(bonus=round(data.bonus,2),
#          bonus=bonus %|% 0,
#          cost=round(bonus*4/3,2)) %>%
#   write_csv(here(data_location, "player_payments.csv")) %>% select(id,bonus) %>% write_csv(here(data_location,"for_prolific.csv"))

@@

d.games <- read_csv(here(data_location, 'games.csv')) %>% 
  rename(gameId = `_id`) %>% 
    filter(createdAt >= date_start)

d.players <- read_csv(here(data_location, 'players.csv')) %>% 
  select(playerId=`_id`,role=data.role)

d.chat.raw <- read_csv(here(data_location, 'rounds.csv'), guess_max=10000) %>%
  filter(createdAt >= date_start) %>%
  mutate(data.chat = ifelse(is.na(data.chat), '{}', data.chat)) %>%
  rename(row_id = `_id`) %>%
  mutate(data.chat = map(data.chat, .f = ParseJSONColumn)) %>%
  unnest(data.chat) %>% 
  select( -ends_with('response'), -ends_with('time')) %>%
  rename_with(~ gsub("data.", "", .x, fixed = TRUE)) %>% 
  write_csv(here(data_location, 'raw_chat.csv'))

d.round_results.raw <- read_csv(here(data_location,'rounds.csv'),guess_max=10000) %>% 
  filter(createdAt >= date_start) %>% 
  rename_with(~ gsub("data.", "", .x, fixed = TRUE)) %>% 
  rename_with ( ~ gsub("room", "player", .x, fixed=T)) %>% 
    rename_with ( ~ gsub("player", "player_", .x, fixed=T)) %>% 
    rename_with ( ~ gsub("response", "_response", .x, fixed=T)) %>% 
  rename_with( ~ gsub("time", "_time", .x, fixed=T)) %>% 
  select(-chat) %>% 
  gather(key, value, starts_with('player')) %>% 
  separate(key, into = c('blah', 'playerId', 'info')) %>% 
  spread(info, value) %>% 
  select(-blah) %>% 
  select(-stageIds,-index,-createdAt,-submitted) %>% 
  filter(!is.na(response)) %>% 
  mutate(time=as.numeric(time)/1000) %>% 
  mutate(targets=map(targets, .f=ParseJSONColumn)) %>% 
  unnest(targets) %>% 
  mutate(image = gsub('/experiment/', '', image, fixed=TRUE),
        image = gsub('.jpeg', '', image, fixed=TRUE)) %>% 
  pivot_wider(names_from=label, names_prefix="box_", values_from=image) %>% 
    mutate(payoffs=map(payoffs, .f=ParseJSONColumn)) %>%
  unnest(payoffs) %>% 
  mutate(AA=ifelse(role=="p1", AA.p1, AA.p2),
         AB=ifelse(role=="p1", AB.p1, AB.p2),
         BA=ifelse(role=="p1", BA.p1, BA.p2),
         BB=ifelse(role=="p1", BB.p1, BB.p2)) %>% 
  write_csv(here(data_location, 'raw_results.csv'))

@@

# Metrics
Paid $2.50 for 15 minutes with up to $4 bonus stated.

Sigh for those couple games.

```{r}
d.round_results <- read_csv(here(data_location,"raw_results.csv"))

summary <- d.round_results %>% group_by(repNum, gameId) %>% 
           mutate(time= time %|% 180) %>% 
  summarize(max_time=max(time)) %>% 
  group_by(gameId) %>% 
  summarize(total_time=sum(max_time)/60,
            num_rounds=max(repNum))

summary

```
```{r}

#ggplot(d.round_results, aes(x=repNum, y=time, color=playerId))+geom_point()

Some groups come close to maxxing bonuses

```{r}
pairs <- d.round_results %>% select(playerId,gameId) %>% unique()
d.players <- read_csv(here(data_location, 'players.csv')) %>% select(playerId=`_id`,data.bonus) %>% filter(!is.na(data.bonus)) %>% left_join(pairs) %>% arrange(gameId)

d.players
```

Number of utterances

pre-chat -- really we want word count not utterances, but eh. 
From skimming people do talk some. 
```{r}
#this is a sloppy way to split, but eh, 
chat <- read_csv(here(data_location, "raw_chat.csv")) %>% filter(!is.na(text)) %>% filter(is.na(targets))

chat %>% group_by(gameId, playerId) %>% tally()
```

```{r}
chat <- read_csv(here(data_location, "raw_chat.csv")) %>% filter(!is.na(text)) %>% filter(!is.na(targets))

chat %>% group_by(gameId, playerId) %>% tally() %>% full_join(d.players)

When they talk

```{r}
chat %>% group_by(gameId, playerId, repNum) %>% tally() %>% filter(n>0) %>% 
  ggplot(aes(x=repNum, y=playerId, color=gameId))+geom_point()

```
(Full chat transcript at bottom)

# What do people choose
   "AA":Best for P1
   "BB":Best for P2

Looks like there's convergence by 20 for the groups that converge, but it may not be obvious they have -- 40 rounds looks right.

@@

Player 2 prefers option B, player 1 prefers action A.

@@

# What do they say about the game

```{r}
  comments <- read_csv(here(data_location,'exit.csv')) %>% select(playerId, gameId, human, workedWell, fair, chatUseful) %>% mutate(gameId=str_sub(gameId, 0,2),playerId=str_sub(playerId, 0,2)) %>% filter(!is.na(gameId)) %>% arrange(gameId)

comments %>% select(playerId, human, workedWell)

comments %>% select(playerId,fair)

comments %>% select(playerId, chatUseful)

```
# Chat

```{r}
read_csv(here(data_location, "raw_chat.csv")) %>% filter(!is.na(text)) %>% mutate(gameId=str_sub(gameId, 0,2),playerId=str_sub(playerId, 0,2)) %>% 
  select(gameId, playerId, repNum, text) %>% kable()

>>>>

---
title: "Study 1"
output:
  html_document: 
    toc: true
---
TODO notes:

 - get empirica time recording to behave (grumble)
 - read feedback
 - remove incomplete game(s)

# Study 1 notes

2x2 study of BoS vs PD crossed with chat or no-chat. All did 40 trials. All did a 3 minute "turing-test" free chat at the start. Run Jan 7. Target was 20 pairs in each condition.

@@

##Data import constants
data_location="data/study1_220107"

date_start=lubridate::ymd('2022-01-07')

@@

# d.players <- read_csv(here(data_location, 'players.csv')) %>%
#   rename(playerId=`_id`) %>%
#   select(data.bonus, playerId,id) %>%
#   mutate(bonus=round(data.bonus,2),
#          bonus=bonus %|% 0,
#          cost=round(bonus*4/3,2)) %>%
#   write_csv(here(data_location, "player_payments.csv")) %>% select(id,bonus) %>%
#   filter(bonus>0) %>% write_csv(here(data_location,"for_prolific.csv"))

```{r}

d.treatments <- read_csv(here(data_location, 'treatments.csv')) %>% 
  rename(treatmentId=`_id`) %>% 
  select(treatmentId, name) %>% 
  separate(name, c("game_cond", "chat_cond"))

d.games <- read_csv(here(data_location, 'games.csv')) %>% 
  rename(gameId = `_id`) %>% 
  left_join(d.treatments) %>% 
    filter(createdAt >= date_start) %>% 
  select(gameId,playerIds,game_cond,chat_cond)

d.gameplayers <- d.games %>% separate(playerIds, c("p1","p2")) %>% 
  pivot_longer(p1:p2, values_to="playerId") %>% 
  select(-name)

d.players <- read_csv(here(data_location, 'players.csv')) %>% 
  select(playerId=`_id`,role=data.role, data.bonus) %>% 
  left_join(d.gameplayers)

@@

d.chat.raw <- read_csv(here(data_location, 'rounds.csv'), guess_max=10000) %>%
  filter(createdAt >= date_start) %>%
  mutate(data.chat = ifelse(is.na(data.chat), '{}', data.chat)) %>%
  rename(row_id = `_id`) %>%
  mutate(data.chat = map(data.chat, .f = ParseJSONColumn)) %>%
  unnest(data.chat) %>% 
  select( -ends_with('response'), -ends_with('time'), -ends_with('payoff'), -ends_with('role')) %>%
  rename_with(~ gsub("data.", "", .x, fixed = TRUE)) %>% 
  left_join(d.games) %>% 
  write_csv(here(data_location, 'raw_chat.csv'))

d.round_results.raw <- read_csv(here(data_location,'rounds.csv'),guess_max=10000) %>% 
  filter(createdAt >= date_start) %>% 
  rename_with(~ gsub("data.", "", .x, fixed = TRUE)) %>% 
  rename_with ( ~ gsub("room", "player", .x, fixed=T)) %>% 
    rename_with ( ~ gsub("player", "player_", .x, fixed=T)) %>% 
    rename_with ( ~ gsub("response", "_response", .x, fixed=T)) %>% 
  rename_with( ~ gsub("time", "_time", .x, fixed=T)) %>% 
  select(-chat) %>% 
  gather(key, value, starts_with('player')) %>% 
  separate(key, into = c('blah', 'playerId', 'info')) %>% 
  spread(info, value) %>% 
  select(-blah) %>% 
  select(-stageIds,-index,-createdAt,-submitted) %>% 
  filter(!is.na(response)) %>% 
  mutate(time=as.numeric(time)/1000) %>% 
  mutate(targets=map(targets, .f=ParseJSONColumn)) %>% 
  unnest(targets) %>% 
  mutate(image = gsub('/experiment/', '', image, fixed=TRUE),
        image = gsub('.jpeg', '', image, fixed=TRUE)) %>% 
  pivot_wider(names_from=label, names_prefix="box_", values_from=image) %>% 
    mutate(payoffs=map(payoffs, .f=ParseJSONColumn)) %>%
  unnest(payoffs) %>% 
  mutate(AA=ifelse(role=="p1", AA.p1, AA.p2),
         AB=ifelse(role=="p1", AB.p1, AB.p2),
         BA=ifelse(role=="p1", BA.p1, BA.p2),
         BB=ifelse(role=="p1", BB.p1, BB.p2)) %>% 
  left_join(d.games) %>% 
  write_csv(here(data_location, 'raw_results.csv'))

@@

# Game length
Estimated 15 mins total including intro/exit/waiting turing etc

How long did people spend playing? (Not counting intro chat round)

```{r total-time}
# game KxJzRQeo5HikZxreo, player BkAWA2P83AnBmRcif has consistently unreasonable times (3300+, should be <180, so something's messing up)

d.round_results %>% filter(gameId=="KxJzRQeo5HikZxreo") %>% select(repNum, time, playerId) %>% arrange(time)
d.round_results <- read_csv(here(data_location,"raw_results.csv"))

summary <- d.round_results %>% group_by(repNum, gameId, game_cond, chat_cond) %>% 
  filter(time<181) %>% 
  summarize(max_time=max(time)) %>% 
  group_by(gameId, game_cond, chat_cond) %>% 
  summarize(total_time=sum(max_time)/60,
            num_rounds=max(repNum)) %>% 
  filter(num_rounds==39)

ggplot(summary, aes(x=str_c(game_cond," ", chat_cond), y=total_time, color=str_c(game_cond," ", chat_cond)))+geom_jitter(width=.1)+  stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width=.3), size=.5,color="black")+
  labs(title="Game time in min", y="mins", x="condition")+theme(legend.position = "none")
```

# Bonuses

Note that bonuses are not directly comparable between BoS & PD! 
But it looks like chat helps in BoS and not in PD.

```{r}
pairs <- d.round_results %>% select(playerId,gameId) %>% unique()
bonuses <- d.players %>%inner_join(pairs) %>%  select(playerId,data.bonus, chat_cond, game_cond) %>% filter(!is.na(data.bonus)) %>% left_join(pairs) %>% arrange(gameId)

ggplot(bonuses, aes(x=str_c(game_cond," ", chat_cond), y=data.bonus, color=str_c(game_cond," ", chat_cond)))+geom_jitter(width=.1)+
  labs(title="Bonus earned", y="bonus", x="condition")+  stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width=.3), size=.5,color="black")+theme(legend.position = "none")+scale_y_continuous(limits=c(0,6))
```

# Pre-chat 
```{r}
#this is a sloppy way to split, but eh, 
chat <- read_csv(here(data_location, "raw_chat.csv")) %>% filter(!is.na(text)) %>% filter(is.na(targets)) %>% 
  mutate(words=str_count(text, "\\w+")) %>%  group_by(gameId, playerId, chat_cond, game_cond) %>% summarize(words=sum(words))

ggplot(chat, aes(x=str_c(game_cond," ", chat_cond), y=words))+geom_jitter(width=.1)+
  labs(title="Words produced in pre-chat", y="words", x="condition")
```

# During chat

This chat is raw. There are outliers that have been chopped off. 
People talk more during BoS than PD.

```{r}
game_chat <- read_csv(here(data_location, "raw_chat.csv")) %>% filter(!is.na(targets)) %>% filter(chat_cond=="chat") %>% 
  mutate(words=str_count(text, "\\w+") %|% int(0)) %>%  group_by(gameId, playerId, game_cond, repNum) %>% summarize(words=sum(words))

chat_by_game <- game_chat %>% group_by(gameId, game_cond, repNum) %>% summarize(words=sum(words))

is_chat <- chat_by_game %>% mutate(is.chat=ifelse(words>0, 1,0)) %>% group_by(game_cond, repNum) %>% summarize(pct_chat=mean(is.chat))

ggplot(game_chat, aes(x=repNum, y=words, color=game_cond))+geom_jitter(width=.1, size=1, alpha=.2)+facet_wrap(~game_cond)+scale_y_continuous(limits=c(0,30))+
  geom_smooth()+
  labs(title="Words produced per round per player", y="words")

ggplot(chat_by_game, aes(x=repNum, y=words, color=game_cond))+geom_jitter(width=.1, size=1, alpha=.2)+facet_wrap(~game_cond)+scale_y_continuous(limits=c(0,30))+
  geom_smooth()+
  labs(title="Words produced per round per game", y="words")

ggplot(is_chat, aes(x=repNum, y=pct_chat, color=game_cond))+geom_point()+
  labs(title="Pct games who said anything", y="pct")
```
Currently open questions -- is that game-related chat, or is it just that it's a friendlier game? 
Does the chatting help?

To look at if chatting helps -- we can compare forced no-chat to chat (see bonuses above). We can also compare used chat (0/1 or amount) within those that could chat.

Options for dependent variable are bonus (although there's some noise there) or option chosen.

```{r}

group_chat <- chat_by_game %>% mutate(is.chat=ifelse(words>0, 1,0)) %>% group_by(game_cond, gameId) %>% summarize(pct_chat=mean(is.chat))

all <- d.players %>% left_join(group_chat) %>% filter(data.bonus>0)

ggplot(all, aes(x=pct_chat, y=data.bonus, color=game_cond))+geom_point()

```
Looks like chatting helps for BoS, doesn't get used much for PD.

# What do people choose

In BoS: P1 prefers AA to BB, P2 prefers BB to AA. AB and BA are bad for both.

In PD:

@@

@@
